\chapter{Product information}
%Reducing the spacing from the title
\vspace{-6em}


\section{Identification}
MyFire is a downloadable application for your smartphone. All you need is a
smartphone with an internet connection. It will automatically track your
location and synchronize you with the nearest fire department. This app is
running on android for the moment by later it will be upgraded for other
operating systems. All the central stations will be equipped with our software
which keeps track of all the reports by the app. The registered data will be
saved on our servers as backup and only be accessed by our team. The software is
running on Windows and IOS and our servers on Linux.

\section{Copyright}

All rights are preserved by our company. All registered data will be saved and
be prohibited for public media. 

\section{Trademark notices}

Microsoft, Windows, Windows NT, Windows Server, Apple, Macintosh, Mac OS.

\section{Restrictions}

Restrictions on copying or distributing the software and its associated
documentation.

\section{Warranties}

The smartphone application is a free downloadable for anybody. The tracking
software for the central stations is an issue-free running program with very
simple and purposeful interface. Any issue can be directly reported and will be
investigated.

\section{Contractual obligations}

It is our obligation for a proper running program. Any issue will be recorded,
examined and resolved.

\section{Disclaimers}

We do not take responsibility for misuse of our application. This program is
only for emergency situations.

\section{Contact}
\begin {flushleft}
Jeff Whitehouse
\\[5pt]
Email: jeff.whitehouse.001@student.uni.lu
\\[8pt]
Mike Dos Santos Loureiro
\\[5pt]
Email: mike.dossantos.001@student.uni.lu
\\[8pt]
Maxim Oykine
\\[5pt]
Email: maxim.oykin.001@student.uni.lu
\end {flushleft}